The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-24 paper/ms.tex
jofre papers

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars which can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}. As well as asteroseismology, by also using optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}. Likewise by combining with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice means requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark},  parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}.

>>>>

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars which can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}. As well as asteroseismology, by also using optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}. Likewise by combining with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice means requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark},  parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 34~FGK stars have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}.
